Title field: summary

### 2021-01-18 inst/examples/title.Rmd
ok

```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=16, fig.height=10}
p <- top_plot(df, "title", ntop = ntop) +
       scale_y_log10() +
       labs(y = "Entries (n)", title = Top titles)
print(p)
```

>>>>

```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
library(ggplot2)
p <- top_plot(df, "title", ntop = ntop) +
       scale_y_log10() +
       labs(y = "Entries (n)", title = "Top titles")
print(p)
```
